\input{Templates/Layout Main}
\input{Templates/Preambles}
\input{Templates/Section Templates}

\begin{document}
    \pagestyle{headerName}

    \vspace*{-0.3cm}

    \adjustbox{valign=t}{\begin{minipage}{0.4\textwidth}
        \begin{tcolorbox}[
            height=0.99\textheight, 
            grow to left by=0.3cm, 
            colback=graybox,
            colframe=graybox,
            arc=0mm
        ]
           \sections{CONTACT}

           \EmailID{anandsugan218@gmail.com}
           
           \LinkedIn
                {http://www.linkedin.com/in/anandhasivam-sambathkumar-052629224}
                {Anandhasivam-Sambathkumar}

           \GitHub
                {http://github.com/AnandhaSivam-00}
                {github.com/AnandhaSivam-00}

           \phoneNo{+91 6383499910}

           \address
                {3/112, Aathikkadu}
                {Savakkattupalayam(PO)}
                {Avinashi(TK), Tiruppur - 638 460}
                {Tamilnadu, India}

           \par\noindent\dotfill
           \vspace*{-0.3cm}
           
           \sections{EDUCATION}

           \education
                {B.E - Computer Science and Engineering}
                {K S Rangasamy College of Technology, \\ Tiruchengode}
                {2021 - 2025}
                {CGPA}
                {8.88}
           \education
                {HSC}
                {Kumutha Matriculation and Higher Secondary School, Nambiyur}
                {2020 - 2021}
                {Percentage}
                {90.17\%}
           \education
                {SSLC}
                {Government Higher Secoundary School, Savakkattupalayam}
                {2018 - 2019}
                {Percentage}
                {88.2\%}

           \vspace*{-0.7cm}
           \par\noindent\dotfill
           \vspace*{-0.2cm}

           \sections{AREA OF INTEREST}

           \areaOfInterest
                {3}
                {{"Data Analytics"},{"Web Development"},{"Testing"}}
                {71}
           \vspace*{-0.3cm}
           \par\noindent\dotfill
           \vspace*{-0.2cm}

           \sections{SKILL SETS}
           \vspace*{-0.1cm}
           \skills
                {C, Java, Python, HTML5, CSS}
                {SQL, PostgreSQL}
                {Spreadsheets, PowerBI, Metabase, LaTeX, MS Word, PowerPoint, Canva}
                {71}

           \vspace*{-0.5cm}
           \sections{LANGUAGES KNOWN}
           \vspace*{0.2cm}

           \languages{Tamil}{90}
           \languages{English}{60}
           \languages{Kannada}{40}
        \end{tcolorbox}
    \end{minipage}}
    \adjustbox{valign=t}{\begin{minipage}{0.5\textwidth}
        \begin{tcolorbox}[
            height=0.982\textheight, 
            grow to right by=1.5cm, 
            colback=white,
            colframe=white,
            arc=0mm
        ]
            \vspace*{-0.01cm}
            \sections{CAREER OBJECTIVE}
            \vspace*{-0.05cm}
            \objective{Passionate and enthusiastic student with a strong desire to gain hands-on experience in the industry. I aspire to expand my knowledge, develop a professional network, and gain practical insights. I can use my skills and efforts to contribute to the success of the organization.}

           \par\noindent\dotfill
           \vspace*{-0.2cm}

           \sections{WORK EXPERIENCE}
           \vspace*{-0.1cm}
           \workex
                {Data Analytics Intern}
                {Learn Basics}
                {Jan 2024 - Apr 2024}
                {https://learnbasics.fun/}
                {
                    \begin{itemize}[itemsep=0.007cm,leftmargin=*]
                        \item[-] Crafted comprehensive reports and presentations for individual schools, leveraging LaTeX, to showcase student performance based on LaPIS test results.
                        \item[-] Develop and maintain the Metabase dashboards, utilizing PL/pgSQL queries to extract actionable insights from raw data for each school.
                    \end{itemize}
                }
                {https://github.com/AnandhaSivam-00/Advanced-SQL-Intern}

           \par\noindent\dotfill

           \vspace*{-0.4cm}
                
            \sections{MINIPROJECTS}
            \nohyphens{
            \begin{itemize}[itemsep=0.2pt, leftmargin=0.5cm]
                \item Developed React and Node.js based food ordering website with stripe integration.
                \item Designed dashboards using PowerBI for analyzing the US Super Market sales and college Code-A-Thon student participation.
                \item Developed Java Swing based simple password manager to store the user passwords in the MySQL database. 
            \end{itemize} }
            
            \vspace*{-0.2cm}
            \par\noindent\dotfill
            \vspace*{-0.4cm}
            
            \sections{ACHIEVEMENTS}
            \begin{itemize}[itemsep=0.2pt, leftmargin=0.5cm]
                \item Secured the 2nd position in “Code Astra 2022” conducted by IIT Bombay.
                \item Participated in the “Innovate India Coding Championship 2022” and selected for 2nd round.  
            \end{itemize}

            \vspace*{-0.2cm}
            \par\noindent\dotfill
            \vspace*{-0.4cm}
            
            \sections{VOLUNTEERING}
            \begin{itemize}[itemsep=0.2pt, leftmargin=0.5cm]
                \item Media Lead in inter-college ASCII Association. 
            \end{itemize}

            \vspace*{-0.2cm}
            \par\noindent\dotfill
            \vspace*{-0.4cm}
            
            \sections{CERTIFICATIONS}
            \nohyphens{
            \begin{itemize}[itemsep=0.2pt, leftmargin=0.5cm]
                \item Coursera Professional Certificate in Data Analytics specialization.
                \item Completed “Databases and SQL for Data Science using Python” in Coursera.
                \item Completed “Acquiring Data” with a gold category certificate in NASSCOM.
                \item Completed “Programming in Java” with an Elite + Silver certificate in NPTEL.  
            \end{itemize} }
        \end{tcolorbox}
    \end{minipage}}
    
\end{document}